PM Mungbean meta-analysis

### 2021-02-01 02_Preliminary_analysis.Rmd
Simplify and correct introduction, clearer headings, remove dupplicate tables

The data explored in the `PM_MB_dat` data frame is a list of mean values from each treatment in each respective experiment.
These preliminary analyses will describe the data and then investigate any change in mungbean yields which is attributable to the fungicide treatment.

All fungicide AI treatments are still contained in the `PM_MB_dat` data, so filtering the data might be necessary to only inspect DMI treatments.

### Descriptive statistics  
#### Spatio-temporal variation

Let's look at how many trials were undertaken each season in trials including DMI fungicides.

```{r FinalTrialsForInclusion1}
tmp1 <- PM_MB_dat %>%
   distinct(trial_ref, location, year) %>%
   arrange(year)
table(tmp1$year)
```

Also the location of the trials including DMI fungicides.

@@

#### Mean yield

What is the variation in yield over all the trials in the no spray control.

```{r ControlYield_AllTrials}
PM_MB_dat %>%
   filter(fungicide_ai == "control") %>%
   summarise(
      mean_yield = mean(grain_yield.t.ha. * 1000),
      median_yield = median(grain_yield.t.ha. * 1000),
      minimum_yield = min(grain_yield.t.ha. * 1000),
      maximum_yield = max(grain_yield.t.ha. * 1000),
      yield_stdev = sd(grain_yield.t.ha. * 1000),
      yield_SE = sd(grain_yield.t.ha. * 1000) /
         sqrt(n())
   ) %>%
   kable(align = 'c',
         caption = "Average yield statistics for no spray control plots")
```

Mean yields in DMI fungicide treated plots
```{r Yield_DMITrials}
PM_MB_dat %>%
   filter(fungicide_ai == "tebuconazole" |
             fungicide_ai == "propiconazole")%>%
   summarise(mean_yield = mean(grain_yield.t.ha.*1000),
             median_yield = median(grain_yield.t.ha. * 1000),
             minimum_yield = min(grain_yield.t.ha.*1000),
             maximum_yield = max(grain_yield.t.ha.*1000),
             yield_stdev = sd(grain_yield.t.ha. * 1000),
             yield_sterr = sd(grain_yield.t.ha.*1000)/(sqrt(length(grain_yield.t.ha.))))%>%
   kable(align = 'c',
   caption = "Average yield statistics for DMI fungicide treated plots")

```

Trial mean yields in all fungicide treated plots
```{r Yield_AllTrials}
PM_MB_dat %>%
   group_by(trial_ref, location, year)%>%
   summarise(mean_yield = mean(grain_yield.t.ha.*1000),
             median_yield = median(grain_yield.t.ha. * 1000),
             minimum_yield = min(grain_yield.t.ha.*1000),
             maximum_yield = max(grain_yield.t.ha.*1000),
             yield_stdev = sd(grain_yield.t.ha. * 1000),
             yield_sterr = sd(grain_yield.t.ha.*1000)/(sqrt(length(grain_yield.t.ha.))))%>%
   arrange(yield_sterr) %>%
   kable(align = 'c',
   caption = "Average yield statistics for DMI fungicide treated plots")

```

#### Full trial summary

Let's inspect a summary of both powdery mildew severity and grain yield for trials including DMI fungicides.

>>>>

The data explored in the `PM_MB_dat` data frame is a clean data frame focusing on trials which met the selection criteria and the treatments testing DMi fungicides (tebuconazole / propiconazole) or no spray controls.

### Spatio-temporal variation  
#### Trial seasons
Let's look at how many trials were undertaken each season in trials including DMI fungicides.

```{r FinalTrialsForInclusion1}
tmp1 <- PM_MB_dat %>%
   distinct(trial_ref, location, year) %>%
   arrange(year)
table(tmp1$year)
```
#### Trial locations
The location of the trials including DMI fungicides.

@@

#### Full trial summary
Let's inspect a summary of both powdery mildew severity and grain yield for trials including DMI fungicides.
